---
title: "p8105_hw1_pw2550"
author: Ada Wang
date: "2026-03-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# library
library(moderndive)
library(ggplot2)
```

# Problem 1
```{r data import}
data("penguins")

data("early_january_weather")
```

* The variables in the "early_january_weather" dataset contains the following variables:
  * origin: Weather station. Named origin to facilitate merging with nycflights13::flights data.
  * year, month, day, hour: Time of recording.
  * temp, dewp: Temperature and dewpoint in F.
  * humid: Relative humidity.
  * wind_dir, wind_speed, wind_gust: Wind direction (in degrees), speed and gust speed (in mph).
  * precip: Precipitation, in inches.
  * pressure: Sea level pressure in millibars.
  * visib: Visibility in miles.
  * time_hour: Date and hour of the recording as a POSIXct date.

* This data contains `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)` variables.

* The mean temperature in early January is `r mean(early_january_weather$temp)` Fahrenheit degrees.

```{r plot}
temp_plot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point()

temp_plot

## save
ggsave("scatterplot of temperature.pdf")
```

* The temperature rises as the time goes. 

# Problem 2 
```{r data frame}
library(tidyverse)

set.seed(100)

sample <- rnorm(10)

df <- data.frame(
  vec_sample = sample,
  vec_logical = sample > 0,
  vec_character = sample(letters, 10),
  vec_factor = factor(sample(c("A", "B", "C"), 10, replace = TRUE))
)

df
```

```{r mean, results = "hide"}
vec_sample_mean <- mean(df$vec_sample)
vec_logical_mean <- mean(df$vec_logical)
vec_character_mean <- mean(as.numeric(df$vec_character))
vec_factor_mean <- mean(as.numeric(df$vec_factor))
```

* I can pull out the mean of vec_sample and vec_logical at the beginning, but failed in the others.
  * vec_sample is numeric at the first place and it makes sense that it can be pulled out the mean.
  * vec_logical shows that TRUE is 1 and FALSE is 0, therefore the average is 0.5 since the sample data are normal distributed.
* After converting to the numeric variables, all values in vec_character are converted to NA and their mean is NA as well.
* After converting to the numeric variables, the levels in vec_factor are converted to be 1, 2 and 3. Therefore their mean can be calculated.


