---
title: "p8105_hw1_pw2550"
author: Ada Wang
date: "2026-03-15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1
```{r}
library(moderndive)
data("penguins")

data("early_january_weather")
```

* The variables in the "early_january_weather" dataset contains the following variables:
  * origin: Weather station. Named origin to facilitate merging with nycflights13::flights data.
  * year, month, day, hour: Time of recording.
  * temp, dewp: Temperature and dewpoint in F.
  * humid: Relative humidity.
  * wind_dir, wind_speed, wind_gust: Wind direction (in degrees), speed and gust speed (in mph).
  * precip: Precipitation, in inches.
  * pressure: Sea level pressure in millibars.
  * visib: Visibility in miles.
  * time_hour: Date and hour of the recording as a POSIXct date.

* This data contains `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)` variables.

* The mean temperature in early January is `r mean(early_january_weather$temp)` Fahrenheit degrees.